Four Models for Severe Weather Deaths

### 2017-05-11 presentation.tex
Changes to ZIP slides

	\section{Zero Inflated Poisson Model}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		The zero inflated Poisson model has two parameters p, the probability of a structural zero, and $\lambda$, the usual Poisson parameter. 
		For a single X, the probability density is:
		$$pI_{X=0}(X) + (1-p)\frac{\lambda^Xe^-\lambda}{X!}$$
	\end{frame}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		One way to write the likelihood is as follows:
		$$\prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]$$
		Bayarri, Berger, and Datta (2008)\footnotemark suggest using the prior distribution $\pi(\lambda, p) \propto \frac{1}{\sqrt{\lambda}}I(0<p<1)$. This gives us the following posterior:
		$$\prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[(1-p)\frac{e^{-\lambda}\lambda^{x_i - 1/2}}{x_i!}\bigg]$$
		\footnotetext[1]{Bayarri, M., Berger, J., Datta, G. (2008). Objective testing of Poisson versus inflated Poisson models. IMS 	Collections, 3, 105-121.}
	\end{frame}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		We can simplify a bit to get the following conditionals:
		\[
p(\lambda|X, p) \propto \prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[e^{-\lambda}\lambda^{x_i - 1/2}\bigg]
\]

>>>>

	\section{Zero Inflated Poisson Model}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		The zero inflated Poisson model has two parameters p, the probability of a structural zero, and $\lambda$, the usual Poisson parameter. 
		For a single X, the probability density is:
		$$pI_{X=0}(X) + (1-p)\frac{\lambda^Xe^-\lambda}{X!}$$
	\end{frame}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		One way to write the likelihood is as follows:
		$$\prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]$$
		Bayarri, Berger, and Datta (2008)\footnotemark suggest using the prior distribution $\pi(\lambda, p) \propto \frac{1}{\sqrt{\lambda}}I(0<p<1)$. This gives us the following posterior:
		$$\prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\lambda^{-1/2}$$
		\footnotetext[1]{Bayarri, M., Berger, J., Datta, G. (2008). Objective testing of Poisson versus inflated Poisson models. IMS 	Collections, 3, 105-121.}
	\end{frame}
	\begin{frame}
		\frametitle{Zero Inflated Poisson Model}
		We can simplify a bit to get the following conditionals:
		\[
p(\lambda|X, p) \propto \prod_{x_i=0}\bigg[p+(1-p)\frac{e^{-\lambda}\lambda^{x_i}}{x_i!}\bigg]\prod_{x_i \ne 0}\bigg[e^{-\lambda}\lambda^{x_i}\bigg]\lambda^{-1/2}
\]
